Supplement 1

### 2020-09-08 paper/supplement-1.Rmd
change examples of missing data in supplement one.

Data MAR are more likely to occur than data MCAR. Data MAR could arise if
a weighing scale used to measure players' pre- and post-match body mass 
produced more missing values when placed on soft carpet, rather than hard tiles. 
The scale may produce more missing values because of the soft surface. If 
surface type was recorded, data could be considered MAR, because the 
missingness is related to some observed data (i.e., surface), but not related 
to the value of the variable with the missing values itself.

MNAR is when missingness is
related to something unobservable. For example, data MNAR could arise
when, if studying doping, a player was to remove their head and body
hair, to avoid providing a hair sample for testing
[\[4\]](https://www.zotero.org/google-docs/?4Ildjf). In this case, data
is missing (the hair sample), and this information is not captured by
any other variable that was collected (hair length was not recorded).

# Older ideas

For example, if a players' player ratings\--a statistic derived from
many variables in the dataset\--are unavailable for one, or several,
Australian Football matches, despite the individual participating in the
match and the other variables being recorded.

>>>>

Data MAR could arise if a weighing scale used to measure players' pre- and 
post-match body mass produced more missing values when placed on soft carpet, 
rather than hard tiles. If the scales produced more missing values because of 
the softer surface, and surface type was a recorded variable, data would be MAR, 
because the missingness is related to some observed data (i.e., surface), but 
not related to the value of the variable with the missing values itself (i.e., body mass). 
(ref: https://stefvanbuuren.name/fimd/sec-MCAR.html).

Data MNAR is when the missings are related to something unobservable. 
For example, data MNAR could arise when, if studying doping, a player 
was to remove their head and body hair, to avoid providing a hair sample for testing
[\[4\]](https://www.zotero.org/google-docs/?4Ildjf). In this case, data
is missing (the hair sample), and this information is not captured by
any other variable that was collected (hair length was not recorded).
